Improving Software Maintainability through Automated Refactoring of Code Clones

### 2019-09-27 saner/paper.tex
Updates from Overleaf

We analyze the overhead of applying a refactoring in terms of four factors: the size of the clone, the relation between the code fragments in a clone, whether clone fragments create, modify or returns data and the amount of external data that cloned fragments use. We find that the combined volume of similar fragments in a clone is the biggest influencing factor: the majority of duplicates with a total size of 63 or more tokens improve maintainability when refactored. The amount of external data that needs to be passed to the merged location of the duplicate is the other important factor: the majority of clones with more than requiring more than one external parameter decreases maintainability.
\end{abstract}

@@

In this study, we define a technique to detect clones such that they can be automatically refactored. We list a set of criteria that can obstruct refactoring opportunities. We evaluate the relation and location of clones to determine which refactoring techniques are best suited. We introduce a tool that automatically refactors clones by extracting new methods out of duplicated code.

@@

	public void concatTen(String x) {
|\highlightYellow|		x = x + 10; // String concat
|\highlightYellow|		Notifier.notifyChanged(x);
|\highlightYellow|		return x;
	}
}
\end{javacode}}
\end{parcolumns}
\caption{Example of textually equal code fragments that differ in functionality.}
\label{fig:type1}
\end{figure*}

\section{Related Work}
The state-of-the-art in code clone refactoring is the work by Mazinanian et al.~\cite{mazinanian2016jdeodorant}. The authors propose a tool named JDeodorant that can automatically refactor a subset of duplication problems. This tool is based on several studies that look into different aspects of code clone refactoring. In a study by Krishnan et al.~\cite{krishnan2013refactoring} clone refactoring is approached as an optimization problem: how does variability between cloned fragments influence the refactoring techniques required and their implications on system design. Another study by Krishnan et al.~\cite{krishnan2014unification} proposes a list of preconditions for clones to determine their refactorability. This list is revised by Tsantalis et al.~\cite{tsantalis2015assessing}, proposing a set of 8 preconditions that determine whether two duplicated fragments can be refactored.

@@

\section{Defining refactorable clones}
In literature, several clone type definitions have been used to argue about duplication in source code~\cite{roy2007survey}. We discuss how we can define clones such that they can be automatically refactored without side effects on the source code.

@@

\section{Experimental setup}
In this section, we describe the setup of our experiments.

@@

\begin{table}[H]
\centering
\begin{tabular}{@{}llrr@{}}
\toprule
\textit{\textbf{Category}} & \textit{\textbf{Relation}} & \textit{\textbf{Clone Classes}} & \textit{\textbf{Total}} \\ \midrule
\multirow{2}{*}{\begin{tabular}[c]{@{}l@{}}Common\\ Class\end{tabular}} & Same Class & 22,893 & \multirow{2}{*}{31,848} \\ \cmidrule(lr){2-3}
 & Same Method & 8,955 &  \\ \midrule
\multirow{5}{*}{\begin{tabular}[c]{@{}l@{}}Common\\ Hierarchy\end{tabular}} & Sibling & 15,588 & \multirow{5}{*}{20,342} \\ \cmidrule(lr){2-3}
 & Superclass & 2,616 &  \\ \cmidrule(lr){2-3}
 & First Cousin & 1,219 &  \\ \cmidrule(lr){2-3}
 & Common Hierarchy & 720 &  \\ \cmidrule(lr){2-3}
 & Ancestor & 199 &  \\ \midrule
\multirow{4}{*}{Unrelated} & No Direct Superclass & 10,677 & \multirow{4}{*}{20,314} \\ \cmidrule(lr){2-3}
 & External Superclass & 4,525 &  \\ \cmidrule(lr){2-3}
 & External Ancestor & 3,347 &  \\ \cmidrule(lr){2-3}
 & No Indirect Superclass & 1,765 &  \\ \midrule
\multirow{2}{*}{\begin{tabular}[c]{@{}l@{}}Common\\ Interface\end{tabular}} & Same Direct Interface & 7,522 & \multirow{2}{*}{13,074} \\ \cmidrule(lr){2-3}
 & Same Indirect Interface & 5,552 &  \\ \bottomrule
\end{tabular}
\caption{Number of clone classes per clone relation}
\label{tab:relation}
\end{table}

@@

\begin{figure*}
  \includegraphics[width=1\textwidth]{img/tokenvolume}
  \caption{A graph that shows how the size in tokens of the refactored clone affects maintainability.}
  \label{fig:maintainabilityscore}
\end{figure*}

@@

\begin{figure}[H]
  \includegraphics[width=1\columnwidth]{img/arguments}
  \caption{Influence of number of method parameters on system maintainability.}
  \label{fig:arguments}
\end{figure}

@@

\bibliographystyle{ACM-Reference-Format}
\bibliography{references}

>>>>

We analyze the overhead of applying a refactoring in terms of four factors: the size of the clone, the relation between the code fragments in a clone, whether clone fragments create, modify or return data and the amount of external data that cloned fragments use. We find that the combined volume of similar fragments in a clone is the biggest influencing factor: the majority of duplicates with a total size of 63 or more tokens improve maintainability when refactored. The amount of external data that needs to be passed to the merged location of the duplicate is the other important factor: the majority of clones requiring more than one external parameter decrease maintainability.
\end{abstract}

@@

In this study, we define a technique to detect clones such that they can be automatically refactored. We list criteria that obstruct refactoring opportunities. We evaluate the relation and location of clones to determine which refactoring techniques are best suited. We introduce a tool that automatically refactors clones by extracting new methods out of duplicated code.

@@

	public void concatTen(String x) {
|\highlightYellow|		x = x + 10; // String concatenation
|\highlightYellow|		Notifier.notifyChanged(x);
|\highlightYellow|		return x;
	}
}
\end{javacode}}
\end{parcolumns}
\caption{Example of textually equal code fragments that differ in functionality.}
\label{fig:type1}
\end{figure*}

\section{Related Work}
The state-of-the-art in code clone refactoring is the work by Mazinanian et al.~\cite{mazinanian2016jdeodorant}. The authors propose a tool named JDeodorant that can automatically refactor a subset of duplication problems. This tool is based on several studies that look into different aspects of code clone refactoring. In a study by Krishnan et al.~\cite{krishnan2013refactoring} clone refactoring is approached as an optimization problem: how variability between cloned fragments influences the refactoring techniques required and their implications on system design. Another study by Krishnan et al.~\cite{krishnan2014unification} proposes a list of preconditions for clones to determine their refactorability. This list is revised by Tsantalis et al.~\cite{tsantalis2015assessing}, proposing a set of 8 preconditions that determine whether two duplicated fragments can be refactored.

@@

\todo{Add more related work?}

\section{Defining refactorable clones}
In literature, several clone type definitions have been used to argue about duplication in source code~\cite{roy2007survey}. We discuss how we can define clones such that they can be automatically refactored while avoiding changing the functional behavior and other negative side effects on the source code.

@@

\section{Experimental setup}
\todo{This doesn't say anything: explain how the section is organized}
In this section, we describe the setup of our experiments.

@@

\todo{color package}
\begin{table}[H]
\centering
\begin{tabular}{@{}llrr@{}}
\toprule
\textit{\textbf{Category}} & \textit{\textbf{Relation}} & \textit{\textbf{Clone Classes}} & \textit{\textbf{Total}} \\ \midrule
\multirow{2}{*}{\begin{tabular}[c]{@{}l@{}}Common\\ Class\end{tabular}} & Same Class & 22,893 & \multirow{2}{*}{31,848} \\ \cmidrule(lr){2-3}
 & Same Method & 8,955 &  \\ \midrule
\multirow{5}{*}{\begin{tabular}[c]{@{}l@{}}Common\\ Hierarchy\end{tabular}} & Sibling & 15,588 & \multirow{5}{*}{20,342} \\ \cmidrule(lr){2-3}
 & Superclass & 2,616 &  \\ \cmidrule(lr){2-3}
 & First Cousin & 1,219 &  \\ \cmidrule(lr){2-3}
 & Common Hierarchy & 720 &  \\ \cmidrule(lr){2-3}
 & Ancestor & 199 &  \\ \midrule
\multirow{4}{*}{Unrelated} & No Direct Superclass & 10,677 & \multirow{4}{*}{20,314} \\ \cmidrule(lr){2-3}
 & External Superclass & 4,525 &  \\ \cmidrule(lr){2-3}
 & External Ancestor & 3,347 &  \\ \cmidrule(lr){2-3}
 & No Indirect Superclass & 1,765 &  \\ \midrule
\multirow{2}{*}{\begin{tabular}[c]{@{}l@{}}Common\\ Interface\end{tabular}} & Same Direct Interface & 7,522 & \multirow{2}{*}{13,074} \\ \cmidrule(lr){2-3}
 & Same Indirect Interface & 5,552 &  \\ \bottomrule
\end{tabular}
\caption{Number of clone classes per clone relation}
\label{tab:relation}
\end{table}

@@

\todo{Redo plot, explain axes units}
\begin{figure*}
  \includegraphics[width=1\textwidth]{img/tokenvolume}
  \caption{A graph that shows how the size in tokens of the refactored clone affects maintainability.}
  \label{fig:maintainabilityscore}
\end{figure*}

@@

\todo{Redo plot, explain axes units}
\begin{figure}[H]
  \includegraphics[width=1\columnwidth]{img/arguments}
  \caption{Influence of number of method parameters on system maintainability.}
  \label{fig:arguments}
\end{figure}

@@

\bibliographystyle{plain}
\bibliography{references}
